\bibitem{Zha2003} Y. Zha, J. Gao, and S. Ni, ``Use of normalized difference built-up index in automatically mapping urban areas from TM imagery,'' \emph{Int. J. Remote Sens.}, vol. 24, no. 3, pp.~583--594, 2003., doi:

\bibitem{Pesaresi2013} M. Pesaresi, G. Huadong, X. Blaes, D. Ehrlich, S. Ferri, L. Gueguen, et al., ``A global human settlement layer from optical HR/VHR RS data: Concept and first results,'' \emph{IEEE J. Sel. Top. Appl. Earth Obs. Remote Sens.}, vol. 6, no. 5, pp.~2102--2131, Oct. 2013., doi:

\bibitem{Radoux2016} J. Radoux, G. Chom\'{e}, D. Jacques, F. Waldner, N. Bellemans, N. Matton, et al., ``Sentinel-2's potential for sub-pixel landscape feature detection,'' \emph{Remote Sens. (Basel)}, vol. 8, no. 6, p.~488, 2016., doi:

\bibitem{Kuffer2016} M. Kuffer, K. Pfeffer, and R. Sliuzas, ``Slums from space---15 years of slum mapping using remote sensing,'' \emph{Remote Sens. (Basel)}, vol. 8, no. 6, p.~455, 2016., doi:

\bibitem{Wendt2017} L. Wendt, S. Lang, and E. Rogenhofer, ``\emph{Monitoring of refugee and camps for internally displaced persons using Sentinel-2 imagery---A feasibility study},'' GI_Forum, vol.~1, pp.~172--182, 2017, doi:~.

\bibitem{Wurm2017} M. Wurm, M. Weigand, A. Schmitt, C. Geiss, and H. Taubenb\"{o}ck, \emph{``Exploitation of textural and morphological image features in Sentinel-2A data for slum mapping,'' in Proc. Joint Urban Remote Sens. Event}. Dubai, UAE: JURSE, 2017, pp. 1--4, .

\bibitem{Quinn2018} J. A. Quinn, M. M. Nyhan, C. Navarro, D. Coluccia, L. Bromley, and M. Luengo-Oroz, ``Humanitarian applications of machine learning with remote-sensing data: Review and case study in refugee settlement mapping,'' \emph{Philos. Trans. A Math. Phys. Eng. Sci.}, vol. 376, no. 2128, p.~20170363, Sep. 13 2018., doi:

\bibitem{Rasul2018} A. Rasul, H. Balzter, G. R. F. Ibrahim, H. M. Hameed, J. Wheeler, B. Adamu, et al., ``Applying built-up and bare-soil indices from Landsat~8 to cities in dry climates,'' \emph{Land (Basel)}, vol. 7, no. 3, p.~81, 2018., doi:

\bibitem{Braun2019} A. Braun, F. Fakhri, and V. Hochschild, ``Refugee camp monitoring and environmental change assessment of Kutupalong, Bangladesh, based on radar imagery of Sentinel-1 and ALOS-2,'' \emph{Remote Sens. (Basel)}, vol. 11, no. 17, p.~2047, 2019., doi:

\bibitem{Friedrich2020} H. K. Friedrich and J. Van Den Hoek, ``Breaking ground: Automated disturbance detection with Landsat time series captures rapid refugee settlement establishment and growth,'' \emph{Comput. Environ. Urban Syst.}, vol. 82, p.~101499, 2020., doi:

\bibitem{Corbane2021} C. Corbane, V. Syrris, F. Sabo, P. Politis, M. Melchiorri, M. Pesaresi, et al., ``Convolutional neural networks for global human settlements mapping from Sentinel-2 satellite imagery,'' \emph{Neural Comput. Appl.}, vol. 33, no. 12, pp.~6697--6720, 2021., doi:

\bibitem{VanDenHoek2021} J. Van Den Hoek and H. K. Friedrich, ``Satellite-based human settlement datasets inadequately detect refugee settlements: A critical assessment at thirty refugee settlements in Uganda,'' \emph{Remote Sens. (Basel)}, vol. 13, no. 18, p.~3574, 2021., doi:

\bibitem{Gella2022} G. W. Gella, L. Wendt, S. Lang, D. Tiede, B. Hofer, Y. Gao, et al., ``Mapping of dwellings in IDP/refugee settlements from very high-resolution satellite imagery using a mask region-based convolutional neural network,'' \emph{Remote Sens. (Basel)}, vol. 14, no. 3, p.~689, 2022., doi:

\bibitem{Wernicke2023} K. Wernicke, ``Deep learning for refugee camps---Mapping settlement extents with Sentinel-2 imagery and semantic segmentation,'' M.S.~thesis, Dept. Remote Sens., Univ.~Wurzburg, Wurzburg, Germany, 2023. [Online]. Available: \url{https://elib.dlr.de/196349/}

