\documentclass[11pt]{letter}
\usepackage[margin=1in]{geometry}

\signature{Jose Miguel Robles Leyton}
\address{Independent Researcher\\Utah, USA\\jose.m.robles7@gmail.com}

\begin{document}
\begin{letter}{Editor-in-Chief\\IEEE Geoscience and Remote Sensing Letters}

\opening{Dear Editor-in-Chief,}

I am submitting the manuscript entitled ``NDBI Spectral Gap Predicts Refugee
Camp Detectability from Sentinel-2: Environmental Limits at 10\,m
Resolution'' for consideration as a Letter in IEEE Geoscience and Remote
Sensing Letters.

\textbf{Main contribution.} This work demonstrates that the NDBI spectral
gap---the difference in mean Normalized Difference Built-Up Index between
camp and background---explains 83\% of cross-country variation in refugee
camp detectability at Sentinel-2's 10\,m resolution ($r=0.912$, permutation
$p=0.005$, $n=7$ countries, 101 camps, 1689 tiles). This transforms
scattered qualitative observations in the literature into a quantitative,
predictive framework.

\textbf{Why this belongs in GRSL.} The paper addresses a fundamental
question in geoscience and remote sensing: under what environmental
conditions is spectral detection of informal settlements physically
possible? The result---that detectability is an environmental property rather
than an algorithmic one---has direct implications for how the remote sensing
community designs and evaluates settlement mapping pipelines. The concise,
single-finding nature of the contribution is well suited to the Letters
format.

\textbf{Novelty.} No prior work has (1) quantified the relationship between
spectral contrast and detection performance across countries, (2) shown that
CNN classifiers fail below chance at 10\,m cross-country due to physics
limitations, or (3) documented that structural texture features invert
discriminative direction between arid and humid biomes.

This manuscript contains original, unpublished work and is not under
consideration at any other publication. The author accepts the terms and
conditions of submission to IEEE GRSL.

The submission consists of two files with identical scientific content:
the final two-column format and the single-column review format.

\textbf{AI Disclosure.} This work was conducted with substantial
AI assistance, as detailed in the Acknowledgment section of the
manuscript. ChatGPT 5.2 (OpenAI) and Claude Code with Opus 4.6 (Anthropic) were used
iteratively throughout the research process, from conception to
manuscript preparation. All claims were cross-verified against
published literature. The author assumes full responsibility for
the content.

\closing{Sincerely,}

\end{letter}
\end{document}
